Getting mortality from atlantisom: testing calc_Z function II

### 2019-06-11 TestCalcZ2.Rmd
some fixes to rec timing pars

  # G.Fay 2/21/16
  # UGLY code below tries to align fraction of annual yoy with timing of recruitment
  # values in YOY.txt are total YOY that year waiting to recruit.
  # seems to get rid of most of 'issues' - some v.minor survival >1,
  #perhaps due to averaging of survival over toutinc days
  nyrs <- ceiling(max(yoy$Time)/365)
  times <- unique(yoy$Time)
  recstart_temp <- biolprm$recruit_time
  #recstart_temp[,2] <- biolprm$time_spawn[-(grep('#',
  #                     biolprm$time_spawn[,1])),2] + biolprm$recruit_time[,2]
  # was this grep to get rid of a species with #XXX? breaks when there are none
  recstart_temp[,2] <- biolprm$time_spawn[,2] + biolprm$recruit_time[,2]

  #recstart_temp <- recstart_temp[recstart_temp[,1]%in%turnedon$Code,] #bug added codes with no YOY output
  recstart_temp <- recstart_temp[recstart_temp[,1]%in%recruits$group,]
  recruits$frac_recruit <- 0
  for (irow in 1:nrow(recstart_temp)) {
    group <- recstart_temp[irow,1]
    pick <- which(recruits$group == group)

    recstart <- seq(recstart_temp[irow,2],by=365,length.out=nyrs)
    recstart <- recstart[recstart<max(recruits$Time[pick])]
    recend <- recstart + biolprm$recruit_period[irow,2]
    #rec_times <- rbind(rec_times,cbind(group,recstart,recend))

    for (i_rec in 1:length(recstart)) {
      i_tstart <- which(pick==min(pick[recruits$Time[pick]>=recstart[i_rec]]))
      i_tstop <- which(pick==min(pick[recruits$Time[pick]>=recend[i_rec]]))
      if (i_rec == length(recstart)) i_tstop <- length(pick)
      n_t <- 1+i_tstop-i_tstart
      for (i_t in 1:n_t) {
        t_temp <- recruits$Time[pick[i_tstart+i_t-1]]
        num_temp <- t_temp - recstart[i_rec]
        if (i_t>1) {
          if ((recend[i_rec]-t_temp)>toutinc) {
            num_temp <- toutinc
          }
          else {
            num_temp <- recend[i_rec]-(recruits$Time[pick[i_tstart+i_t-2]])
          }
        }
        frac_temp <- max(c(0,num_temp /(recend[i_rec]-recstart[i_rec])))
        recruits$frac_recruit[pick[i_tstart+i_t-1]] <- frac_temp
      }
    }
  }

@@

  #G.Fay 1/6/16, expand to num of recruits
  # Recruit / mg C converted to wet weight in tonnes / redfield ratio of C:N
  recruits$recruits <- recruits$recruits/k_wetdry/biolprm$redfieldcn

>>>>

  # G.Fay 2/21/16
  # UGLY code below tries to align fraction of annual yoy with timing of recruitment
  # values in YOY.txt are total YOY that year waiting to recruit.
  # seems to get rid of most of 'issues' - some v.minor survival >1,
  #perhaps due to averaging of survival over toutinc days
  nyrs <- ceiling(max(yoy$Time)/365)
  times <- unique(yoy$Time)

  # SKG June 2019
  # need to match codes below, this mismatches when biolprm not in same order!!
  #recstart_temp <- biolprm$recruit_time
  #recstart_temp[,2] <- biolprm$time_spawn[-(grep('#',
  #                     biolprm$time_spawn[,1])),2] + biolprm$recruit_time[,2]
  # was this grep to get rid of a species with #XXX? breaks when there are none
  #recstart_temp[,2] <- biolprm$time_spawn[,2] + biolprm$recruit_time[,2]

  #recstart_temp <- recstart_temp[recstart_temp[,1]%in%turnedon$Code,] #bug added codes with no YOY output
  #recstart_temp <- recstart_temp[recstart_temp[,1]%in%recruits$group,]

  # need spawn_period?? if so read out in load_biolprm and merge it here too

  # rectiming is a dataframe with species code, time_spawn (day of year), 
  # recruit_time (number of days), and recruit period (number of days). 
  # we use these to calculate recstart (day of year) and recend (day of year)
  rectiming <- merge(biolprm$time_spawn, biolprm$recruit_time, by = 1)
  rectiming <- merge(rectiming, biolprm$recruit_period, by = 1)
  names(rectiming) <- c("Code", "time_spawn", "recruit_time", "recruit_period")
  rectiming <- rectiming %>%
    mutate(recstart = time_spawn + recruit_time) %>% # possibly + spawn_period
    mutate(recend = recstart + recruit_period)

  recstart_temp <- rectiming[rectiming$Code %in% recruits$group,]

  # do we need this fraction calculation if YOY is annual snapshot?
  # (check output timing of YOY file with tsumout, available in run.prm)
  # can we not just allocate the full YOY to the timestep where they come in?
  # if recstart to recend spans multiple toutinc timesteps then need fraction

  recruits$frac_recruit <- 0
  for (irow in 1:nrow(recstart_temp)) {
    group <- recstart_temp$Code[irow]
    pick <- which(recruits$group == group)

    recstart <- seq(recstart_temp$recstart[irow],by=365,length.out=nyrs)
    recstart <- recstart[recstart<max(recruits$Time[pick])]
    recend <- recstart + recstart_temp$recend[irow]
    #rec_times <- rbind(rec_times,cbind(group,recstart,recend))

    # this part still returns a constant fraction
    # and does not alter Time to change from annual to actual recruitment time
    # still not understanding what this is meant to do
    for (i_rec in 1:length(recstart)) {
      i_tstart <- which(pick==min(pick[recruits$Time[pick]>=recstart[i_rec]]))
      i_tstop <- which(pick==min(pick[recruits$Time[pick]>=recend[i_rec]]))
      if (i_rec == length(recstart)) i_tstop <- length(pick)
      n_t <- 1+i_tstop-i_tstart
      for (i_t in 1:n_t) {
        t_temp <- recruits$Time[pick[i_tstart+i_t-1]]
        num_temp <- t_temp - recstart[i_rec]
        if (i_t>1) {
          if ((recend[i_rec]-t_temp)>toutinc) {
            num_temp <- toutinc
          }
          else {
            num_temp <- recend[i_rec]-(recruits$Time[pick[i_tstart+i_t-2]])
          }
        }
        frac_temp <- max(c(0,num_temp /(recend[i_rec]-recstart[i_rec])))
        recruits$frac_recruit[pick[i_tstart+i_t-1]] <- frac_temp
      }
    }
  }

# Time in YOY does not match recstart-recend period still after this loop

@@

# SKG did this above already in the following line?
  # Get recruits in numbers rather than biomass
  #recruits$recruits <- recruits$recruitsbio / recruits$sum
  #G.Fay 1/6/16, expand to num of recruits
  # Recruit / mg C converted to wet weight in tonnes / redfield ratio of C:N
  #recruits$recruits <- recruits$recruits/k_wetdry/biolprm$redfieldcn
